\bf Estimating the number of clusters using cross-validation

### 2019-01-11 JCGS-R2/cvclust.tex
yeast caption

\begin{figure}
		\centering
	\includegraphics[width=5.7in, height=5.7in]{main_code/data_examples/split_plots.pdf}
	\caption{Yeast data set mean expression profiles. The $5$ clusters found by
  the Gabriel method are on the bottom; Clusters profiled in
  \cite{tavazoie1999systematic} are on the right.}
	\label{fig:5_clusters}
\end{figure}

>>>>

\begin{figure}
		\centering
	\includegraphics[width=5.7in, height=5.7in]{main_code/data_examples/split_plots.pdf}
	\caption{Comparison between  \cite{tavazoie1999systematic} clusters and
    our proposed Gabriel cross-validation clusters for a Yeast gene expression
    time series data set.  The plots on the vertical and horizontal
    show the average expression time series for the \citeauthor{tavazoie1999systematic} 
    clusters (1--4, 7, 8, 14, Other) and the Gabriel clusters (1--5),
    respectively. Plot $(i,j)$ in the grid show the time series average
    in the intersectios of  \citeauthor{tavazoie1999systematic} cluster~$i$
    with Gabriel cluster~$j$, whenever there is overlap. The Gabriel clusters
    capture the same general trends with a smaller number of clusters.
    }
	\label{fig:5_clusters}
\end{figure}
